Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Further updates to §2.1

Networked multimedia deadlines are unusual when compared to other real-time
systems. They are simultaneously flexible and strict: flexible in that the exact
value of the deadline is typically not important, provided it is of the right
order-of-magnitude for the application, but strict in that any particular
deadline provides a cut-off, after which the data arrives too late to be
rendered to the user (although, again, it is not entirely useless, since
it might be used to complete predictive coding state, improving the quality 
of frames decoded later).

@@

Many real-time applications run over TCP today, though TCP offers no partial
reliability service. TCP's full reliability can lead to play-out stalls
when the application is blocked by retransmissions that take too
long. These stalls are one of the primary causes of poor user experience in
streaming applications.
% , and are directly caused by the lack of partial reliability in TCP.
For the applications under scrutiny, a missed frame that fails to deliver by its
deadline is much less disruptive than a stall in play-out.

\textbf{Message-oriented Dependencies:}
The combination of deadlines and partial reliability leads to \emph{dependency
management} as an important transport service.
% There is no point in sending data that cannot be used because it depends on
% previous data that was not received.
In particular, data should never be sent when it relies on a previous
transmission that was never received. Providing this service is complicated by
the two ways in which data can be \emph{useful} to applications: it may itself
be played out, or it may be needed as part of the application's decoding chain.
Interdependencies between frames of video exist within a number of codecs,
including MPEG-1 \cite{le1991mpeg}, and newer codecs such as H.264
\cite{wiegand2003overview}. As an example, we consider MPEG-1 video:
I-frames are independent, while P- and B-frames contain only the changes 
since the previous frame (P) or between frames (B), and so are dependent on
the successful arrival of other frames. An I-frame may not arrive in time
to be played out, but may need to be sent to ensure that dependent P- and
B-frames are useful.

@@

\textbf{Connections and Congestion Control:}
We note the importance of congestion control. Historically, real-time many
applications have required an isochronous channel, that is not subject to
congestion control. This is impractical on the Internet. Further, while
some applications are non-adaptive or constant bit-rate, an increasing
number are either or both of adaptive and variable bit-rate. Users would
be better served by applications that adapt to available bandwidth.

We note that a connection-oriented transport is a lesser requirement for
many real-time multimedia applications. 
Indeed, flexibility to change the destination within a call is beneficial
for applications that support mobile users, and for some forms of multiparty
session.
Maintaining per-connection state at the endpoints is helpful for the
implementation of many forms of congestion control, however. 
Signalling messages indicating start and end of connections can also ease
NAT traversal, and help dynamically manage firewall pinholes, by indicating
when in-network state should be created and can be torn down. 
Accordingly, it is often desirable for the transport to be connection
oriented.

>>>>

Networked multimedia deadlines are unusual when compared to other real-time
systems. They are simultaneously flexible and strict: flexible in that the exact
value of the deadline is typically not important, provided it is of the right
order-of-magnitude for the application, but strict in that any particular
deadline provides a cut-off, after which the data arrives too late to be
rendered to the user (although, again, it is not entirely useless, since
it might be used to complete a predictive coding chain, improving the quality 
of frames decoded later).

@@

Many real-time applications run over TCP today, though TCP offers no partial
reliability service. TCP's full reliability can lead to play-out stalls
when the application is blocked by retransmissions that take too
long. These stalls are one of the primary causes of poor user experience in
streaming applications.
% , and are directly caused by the lack of partial reliability in TCP.
For the applications under scrutiny, a missed frame that is not delivered
by its deadline, while surrounding frames are delivered, is much less
disruptive than a stall in play-out waiting for repair.

\textbf{Message-oriented Dependencies:}
The combination of deadlines and partial reliability makes \emph{dependency
management} an important transport service.
% There is no point in sending data that cannot be used because it depends on
% previous data that was not received.
In particular, data should never be sent when it relies on a previous
transmission that was never received. Providing this service is complicated by
the two ways in which data can be \emph{useful} to applications: it may itself
be played out, or it may be needed as part of the application's decoding chain.
Interdependencies between frames of video exist within a number of codecs.
The original MPEG-1 codec \cite{le1991mpeg} divided video frames into three
types. I-frames were independently encoded, while P- and B-frames contain
only the changes since the previous frame (P), or between frames (B), and so
could only be decoded dependent on the successful arrival of other frames.
Newer codecs, such as H.264 \cite{wiegand2003overview}, use more complex
and sophisticated versions of the same idea. 
A consequence is that the sender might know that a frame will not arrive in
time to be played out, but may need to send it anyway to ensure that the
receiver can decode any dependent frames sent later in the stream.

@@

\textbf{Connections and Congestion Control:}
We note the importance of congestion control. Historically, real-time many
applications have required an isochronous channel, and have not implemented
congestion control. This is impractical on the Internet. Further, while
some applications are non-adaptive or constant bit-rate, an increasing
number are either, or both, of adaptive and variable bit-rate. Users would
be better served by applications that adapt to available bandwidth. This is
especially true of mobile applications, where channel capacity can vary
significantly over time.

We note that a connection-oriented transport is a lesser requirement for
many real-time multimedia applications. 
Indeed, flexibility to change the destination within a call is beneficial
for applications that support mobile users, and for some forms of multiparty
session.
On the other hand, maintaining per-connection state at the endpoints is
helpful for the implementation of many forms of congestion control.
Signalling messages indicating start and end of connections can also ease
NAT traversal, and help dynamically manage firewall pinholes, by indicating
when in-network state should be created and can be torn down. 
Accordingly, it is often desirable for the transport to be connection
oriented.
